Adopting agile software development in the large organizations: A systematic literature review

### 2014-05-19 journal/article.tex
New title

\title{Adopting agile in the large: motivations, success factors and challenges}

@@

Some success factors ...

>>>>

\title{Adopting agile software development in the large organizations:
       A systematic literature review}

@@

The analyzed primary studies brought up several factors that contributed in
success in the transformation. As stated by Research Question 4, we studied what
factors were reported to facilitate the transformation process. We present
factors that the primary studies particularly highlighted as being important in
advancing the transformation process.

* What is our standpoint on recommendations that experience reports give, but
  which were not necessarily tried in the organization?

\begin{table}[h]
    \centering
    \begin{tabular}{ l l }
        \toprule
        Success factors  &  Described in \\
        \midrule
        Training is necessary to achieve change  &  P3, P6, P14, 16, P30  \\
        \bottomrule
    \end{tabular}
    \caption{Summary of investment and resourcing factors that affect
             transformation negatively}
    \label{table:challenges_lackofinvestment}
\end{table}

\subsubsection{Training and coaching}

Training was seen as a strong factor helping the organization to transform.
Several studies stated that training improved the chance of succeeding in the
transformation [P3, 16, P30]. It was even highlighted that the change would have
failed without transformation [P14]. As Benefield [P6] claimed: ``we saw again
and again how training could make the difference between success and failure for
a team''. Training also helped people to become more positively inclined towards
the new model [P16, P37], and at best training made people enhusiastic to change
[P3, P46]. A few cases reported that there was some disinclination to change,
and training would have helped to overcome [P11, P14].
